Titulo

### 2014-10-27 RotacionOutFlows/Paper/ms.tex
continue intro

---------------------------------------------------------------------\\
MISSING: Intro to rotation model (and its analytic aproximation)\\
-----------------------------------------------------------------------\\

---------------------------------------------------------------------\\
MISSING: Intro to the ThinShell outflow model\\
-----------------------------------------------------------------------\\

\section{Theoretical Frame}
In this section we are going to describes the two different models that are used in this project, that are able to reproduce a real and consistent line.\\

>>>>

As it has been described, the main purpose of this project is to mix a rotating galaxy with an external outflow surrounding it and analyze the resulting spectrum. The rotation model for the LAE consists on a sphere with an homogeneous mixture of dust and hydrogen at a constant temperature undergoing a solid-body rotation. The spectrum then depends on the maximum velocity of the sphere, the neutral hydrogen optical depths and the viewing angle. What happens is that photons are emmited from the an homogeneus distribution of gas and escape the sphere after a radiative transfer process that ends at the border.\\

In this model, rotation does not induce any spatial anisotropy in the integrated line flux, the escape fraction or the average number of scatterings, which led to the creation of an analytic approximation for the galaxy spectrum. This mathematical expression helps to minimize the computational costs and lets try with several parameters without spending great amounts of time running the code. \\

After this photons escape the galaxy to empty space, they encounter a thin spherical shell of matter at a certain radius from the center. That material is the outflow of the LAE, created mainly by starbursts which composition is characterized with the parameters of Hydrogen column density and metallicity. Besides its components, the galactic outflow is also defined by an expanding constant velocity that affects the redshift of the photons.\\

As there is a lot of empty space inside the shell, it acts as a reflector of photons. This means, that when one wants to comes out it is most likely to bounce inside the sphere several times before finally escaping. However it is not likely that the photon comes back again inside the galaxy, which helps that the first process does not have to be repeated, and both stages can be treated as consecutive, not simultaneous. \\

\section{Theoretical Frame}
In this section we are going to describe the two different models that are used in this project, that are able to reproduce a real and consistent line.\\
